Constraining gravitational wave amplitude birefringence with GWTC-3

### 2023-03-10 src/tex/ms.tex
Add chi_p plots

\begin{figure}[h]
    \script{corner_GW190521.py}
    \includegraphics[width=\columnwidth]{figures/corner_GW190521.pdf}
    \caption{
        GW190521 posterior on $\kappa$, luminosity distance $d_L$ and inclination $\cos\iota$ from our frequency-dependent (blue) and frequency-independent (orange) birefringence analysis, compared to the GR result (green).
        % The posterior of $\kappa$, luminosity distance $d_L$ and $\cos{\iota}$ for GW190521.
        % Colors in the plot represent the \ac{PE} result with \ac{GR} and the frequency-dependent birefringence, respectively.
        % The 2D contours correspond to the $39.35\%$ ($1\sigma$) and $90\%$ credible levels.
        % This plot shows that frequency-dependent birefringence cannot break the degeneracy between $\kappa$ and $\iota$.
    }
    \label{fig:corner_GW190521}
\end{figure}

>>>>

\begin{figure}[h]
    \script{corner_GW190521.py}
    \includegraphics[width=\columnwidth]{figures/corner_GW190521.pdf}
    \caption{
        GW190521 posterior on $\kappa$, luminosity distance $d_L$ and inclination $\cos\iota$ from our frequency-dependent (blue), compared to the GR result (green).
        The marginalized posterior on $\chi_p$ is shown in the top right panel.
    }
    \label{fig:corner_GW190521}
\end{figure}
